---
layout: page
title: "`r params$title`"
author: "`r params$authorName`"
abstract: "`r params$abstract`"
date: "Report built : `r format(Sys.Date())`"
output: 
  pdf_document:
    latex_engine: default
header-includes: \usepackage{kotex} \usepackage[doublespacing]{setspace} \usepackage{multirow} 
tables: true
params:
  inputData: NA
  title: NA
  authorName: NA
  abstract: NA
  department: NA
  affiliation: NA
  location: NA
  email: NA
  vec.len: 4
  positive: NA
  negative: NA
---

## Author information

Department: "`r params$department`"

Affiliation: "`r params$affiliation`"

Location: "`r params$location`"

E-mail: "`r params$email`"

\newpage

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: pre

# pass parameter 
inputData <- params$inputData

# library
library(knitr)
library(kableExtra)
library(dplyr)
library(shiny)
library(reactable)

# environment 
options(digits = 3)

# function define

hasNeg <- function(i) {
  length(which(i < 0)) > 0
}

hasPos <- function(i) {
  length(which(i > 0)) > 0
}

isValidEmail <- function(i) {
  grepl("\\<[A-Z0-9._%+-]+@[A-Z0-9.-]+\\.[A-Z]{2,}\\>", as.character(i), ignore.case = TRUE)
}

isUniform <- function(i) {
  return(length(unique(table(i))) == 1)
}

isUnique <- function(i) {
  return(length(which(duplicated(i))) == 0)
}
```



# Data description

> Preview of data - Top 5

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: top

if(ncol(inputData) > 7){
  kable(
    t(head(inputData, 5)),
    format = 'latex', 
    longtable = TRUE 
    # booktabs = TRUE
  ) |> 
  kableExtra::kable_styling(
    latex_options = c("scale_down", "repeat_header"),
    repeat_header_continued = "\\textit{(Continued on Next Page...)}"
  )
  
} else{
  head(inputData, 5) |>
  kable()
}


```


> Preview of data - Last 5

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: tail

if(ncol(inputData) > 7){
  kable(
    t(tail(inputData, 5)),
    format = 'latex', 
    longtable = TRUE 
  ) |> 
  kableExtra::kable_styling(
    latex_options = c("scale_down", "repeat_header"),
    repeat_header_continued = "\\textit{(Continued on Next Page...)}"
  )
    
} else{
  tail(inputData, 5) |>
  kable()
}

```

\newpage

# Structure of data

- Data dimension and structure (with example values)

```{r}
#| echo: false
#| label: structure of data using str

data.frame(
  variable = names(inputData),
  class = sapply(inputData, typeof),
  levels = sapply(inputData, class),
  first_values = sapply(inputData, function(x) paste0(head(x, 10), collapse = ", ")),
  row.names = NULL
) |>
  reactable(
    defaultColDef = colDef(format = colFormat(digits = 3))
  )
```

\newpage

# Missing Data Infomation

```{r}
#| label: missing
#| echo: false
#| warning: false
#| message: false

naniar::gg_miss_var(inputData)

ss <- naniar::miss_var_summary(inputData) |> 
  filter(n_miss > 0) 

colnames(ss) <- colnames(ss) |>
  gsub(pattern = "variable", replacement = "Name") |>
  gsub(pattern = "n_miss", replacement = "Count") |>
  gsub(pattern = "pct_miss", replacement = "Percent")

ss |>
  reactable(
    columns = list(
       Percent = colDef(format = colFormat(digits = 2))
    )
  )
```

\newpage

## Removed Data

```{r}
#| echo: false
#| warning: false
#| message: false

ignoreNA <- names(which(colSums(is.na(inputData)) == nrow(inputData)))

if (length(ignoreNA) > 0) {
  HTML(markdown("
    > Columns Below is removed because every rows are NA
  "))
  
  print(ignoreNA)
  inputData <- inputData[, !(names(inputData) %in% ignoreNA)]
} else {
  markdown("> There is not removed Columns")
}
```

\newpage

## Statistics of data

```{r}
#| echo: false
#| label: type for each column

ss <- inputData |>
  skimr::skim() |>
  select(-"n_missing", -"complete_rate")

# rename columns
colnames(ss) <- colnames(ss) |>
  gsub(pattern = "skim_type", replacement = "Variable Type") |>
  gsub(pattern = "skim_variable", replacement = "Variable Name")

ss |>
  reactable(
    defaultColDef = colDef(format = colFormat(digits = 1))
  )
```

\newpage

## Validity

-   email

```{r, echo=FALSE}
if(params$email != "NA"){
  inputData |> 
  dplyr::select(params$emails) |> 
  sapply(isValidEmail)
} else{
  markdown("> There is no input for check Email value")
}
```

-   positive

```{r, echo=FALSE}
#| label: positive
#| echo: false

if(params$positive != "NA"){
  inputData |>
  select(params$positive) |>
  sapply(hasNeg)
} else{
  markdown("> There is no input for check Positive value")
}
```

-   negative

```{r}
#| label: negative
#| echo: false

if(params$negative != "NA"){
  inputData |>
  select(params$negative) |>
  sapply(hasPos)
} else{
  markdown("> There is no input for check Negative value")
} 
```

\newpage

## Distribution

-   unique

```{r, echo=FALSE}
#| label: isUnique
  ss <- inputData |>
  select(everything()) |>
  sapply(isUnique) 

if(length(which(ss))){
  data.frame(
  Variable = names(ss),
  Unique = unname(ss)
  ) |>
  reactable()
} else{
  markdown("> There is not column without duplicated values")
}



```

-   uniform

```{r, echo=FALSE}

  ss <- inputData |>
  select(everything()) |>
  sapply(isUniform) 

if(length(which(ss))){
  data.frame(
  Variable = names(ss),
  Uniform = unname(ss)
) |>
  reactable()
} else{
  markdown("> There is not column without uniformly distributed")
}
```

\newpage

## Correlation

```{r, echo = FALSE, warning = FALSE, message = FALSE}
if (inputData %>% select(where(is.numeric)) %>% length() < 2) {
  markdown("> Correlation plot ignored, because less than 2 column is numeric")
} else {
  ggcorr(inputData)
}
```

\newpage

## Pairplot

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: pair

infer.numeric <- function(i, count = 10) {
  length(unique(i)) > count
}


scatterData <- inputData |> select(where(is.numeric) & where(infer.numeric))

if(ncol(scatterData)> 10){
  markdown("> Most various 10 column selected")
  scatterData <- scatterData |> select(
    names(head(sort(sapply(scatterData, function(i){length(unique(i))}), decreasing = TRUE), 10))
  )
}

if (!(scatterData |> length() > 0)) {
  markdown("> Data is not appropriate for Pairplot")
} else {
  if (nrow(inputData) > 100) {
    markdown("> Number of Row Reduced to 1000")
    scatterData <- scatterData |>
      sample_n(1000)
  }
  scatterData |>
    GGally::ggpairs()
}


```

\newpage

## suggestion

-   check
-   change
-   remove...


