---
title: "`r params$title`"
date: "Report built : `r format(Sys.Date())`"
authors:
  - name: "`r params$authorName`"
    department: "`r params$department`"
    affiliation: "`r params$affiliation`"
    location: "`r params$location`"
    email: "`r params$email`"
abstract: |
  "`r params$abstract`"
output:
  rticles::arxiv_article:
    latex_engine: pdflatex
classoption: landscape
header-includes:
  - \usepackage{longtable}
  - \usepackage{kotex}

params:
  inputData: NA
  vec.len: 4
  positive: NA
  negative: NA
  title: NA
  authorName: NA
  abstract: NA
  department: NA
  affiliation: NA
  location: NA
  email: NA
keywords:
  - data profiling
  - data quality
  - data analysis
  - descriptive statistics
  - data preprocessing
  - data-driven decision-making
---

<!--  ADDITIONAL YAML
abstract: |
  "`r params$abstract`"
bibliography: references.bib
biblio-style: unsrt
-->

\newpage

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: pre

# pass parameter 
inputData <- params$inputData

# library
library(knitr)
library(kableExtra)
library(dplyr)
library(shiny)
library(naniar)
library(skimr)

# environment 
options(digits = 3)
options(knitr.kable.NA = '') 

# function define

hasNeg <- function(i) {
  length(which(i < 0)) > 0
}

hasPos <- function(i) {
  length(which(i > 0)) > 0
}

isValidEmail <- function(i) {
  grepl("\\<[A-Z0-9._%+-]+@[A-Z0-9.-]+\\.[A-Z]{2,}\\>", 
        as.character(i), ignore.case = TRUE)
}

isUniform <- function(i) {
  return(length(unique(table(i))) == 1)
}

isUnique <- function(i) {
  return(length(which(duplicated(i))) == 0)
}
```

# Data description

> Preview of data - First 5 Rows

If the data has more than 7 columns, the rows and columns will be swapped.

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: top

pp <- head(inputData, 5)

if(ncol(inputData) > 7){
 pp <- t(head(inputData, 5))
}

pp %>%
  knitr::kable(
    format = "latex",
    align = "l",
    # booktabs = TRUE,
    longtable = TRUE,
    ) %>%
  kableExtra::kable_styling(
    latex_options = c("scale_down", "repeat_header"),
    repeat_header_continued = "\\textit{(Continued on Next Page...)}"
  )

```

> Preview of data - Last 5 Rows

If the data has more than 7 columns, the rows and columns will be swapped.

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: tail

if(ncol(inputData) > 7){
  knitr::kable(
    t(tail(inputData, 5)),
    format = 'latex', 
    longtable = TRUE 
  ) %>% 
  kableExtra::kable_styling(
    latex_options = c("scale_down", "repeat_header"),
    repeat_header_continued = "\\textit{(Continued on Next Page...)}"
  )
    
} else{
  tail(inputData, 5) %>%
  knitr::kable()
}

```

\newpage

# Structure of data

- Data dimension and structure (with first 5 values)

```{r}
#| echo: false
#| label: structure of data using str


df <- data.frame(
  variable = names(inputData),
  class = sapply(inputData, function(i){
      v <- typeof(i) %>% substr(start = 1, stop = 2)
      if(length(v)>1) return(v[1])
      return(v)
    }),
  levels = sapply(inputData, function(i){
    v <- class(i) %>% substr(start = 1, stop = 2)
    if(length(v)>1) return(v[1]) # multiple class
    return(v)
  }),
  first_values = sapply(inputData, function(x) paste0(head(x, 5), collapse = ", ")),
  row.names = NULL
) 

knitr::kable(df)

# str(inputData, vec.len = params$vec.len)

# data.frame(
#   variable = names(inputData),
#   class = sapply(inputData, typeof),
#   levels = sapply(inputData, class),
#   first_values = sapply(inputData, function(x) paste0(head(x, 5), collapse = ", ")),
#   row.names = NULL
# ) |>
#   kable()
```

\newpage

# Missing Data Infomation

Percentage of missing Data for each column 

```{r}
#| label: missing
#| echo: false
#| warning: false
#| message: false

naniar::gg_miss_var(inputData, show_pct = TRUE)

```

Detailed information for column, that has at least one missing data 

```{r}
#| label: missing2
#| echo: false
#| warning: false
#| message: false

ss <- naniar::miss_var_summary(inputData) |> 
  filter(n_miss > 0) |>
  rename(Name = variable) |>
  rename(Count = n_miss) |>
  rename(Percent = pct_miss) |>
  as.data.frame()

knitr::kable(ss, format = 'latex') |>
  kableExtra::kable_styling(
    position = "center"
  )

```

\newpage

## Removed Data


```{r}
#| label: removed
#| echo: false
#| warning: false
#| message: false

ignoreNA <- names(which(colSums(is.na(inputData)) == nrow(inputData)))

cat("Columns with Every row consisted with NA will be removed.")

if (length(ignoreNA) > 0) {
  cat("Columns below is removed")
  print(ignoreNA)
  inputData <- inputData[, !(names(inputData) %in% ignoreNA)]
} else {
  cat("There is not any removed columns")
}
```

\newpage

## Statistics of data

```{r}
#| echo: false
#| label: type for each column

# ss <- inputData |>
#   skimr::skim() |>
#   select(-"n_missing", -"complete_rate", -"numeric.hist") |>
#   rename(Type = skim_type) |>
#   rename(Name = skim_variable) |>
#   rename(Mean = numeric.mean) |>
#   rename(SD = numeric.sd) |>
#   rename(Min = numeric.p0) |>
#   rename("1Q" = numeric.p25) |>
#   rename(Median = numeric.p50) |>
#   rename("3Q" = numeric.p75) |>
#   rename(Max = numeric.p100)
# #  rename(Max = numeric.p100) |>
# 
# knitr::kable(ss, format = 'latex', longtable = TRUE) |>
#   kableExtra::kable_styling(
#     position = "center"
#   )
  
ss <- inputData %>%
  skimr::skim() %>%
  select(-"n_missing", -"complete_rate", -"skim_type")

# rename columns
colnames(ss) <- colnames(ss) %>%
  # gsub(pattern = "skim_type", replacement = "Variable Type") %>%
  gsub(pattern = "skim_variable", replacement = "Variable Name")

knitr::kable(ss) %>%
  kableExtra::kable_styling(
    latex_options = c("scale_down", "repeat_header"),
    repeat_header_continued = "\\textit{(Continued on Next Page...)}"
  )

```

\newpage

## Validity

<!-- 
- email
NOT PREPARED YET
-->

```{r}
#| echo: false
# if(params$email != "NA"){
#   inputData |> 
#   dplyr::select(params$emails) |> 
#   sapply(isValidEmail)
# } else{
#   cat("> There is no input for check Email value")
# }
```

- positive: check column has positive value (expected all negatives)

```{r}
#| label: positive
#| echo: false

if(params$positive != "NA"){
  inputData |>
  select(params$positive) |>
  sapply(hasNeg)
} else{
  cat("There is no input for check Positive value")
}
```

- negative: check column has negative value (expected all positives)

```{r}
#| label: negative
#| echo: false

if(params$negative != "NA"){
  inputData |>
  select(params$negative) |>
  sapply(hasPos)
} else{
  cat("There is no input for check Negative value")
} 
```

\newpage

## Distribution

- unique

```{r}
#| label: isUnique
#| echo: false

# ss <- inputData |>
#   select(everything()) |>
#   sapply(isUnique) 
# 
# if(length(which(ss))){
#   data.frame(
#     Variable = names(ss),
#     Unique = unname(ss)
#   ) |>
#   kable()
# } else{
#   cat("There is not column without duplicated values")
# }

ss <- inputData %>%
  select(everything()) %>%
  sapply(isUnique) 

if(length(which(ss))){
  data.frame(
  Variable = names(ss),
  Unique = unname(ss)
  ) %>%
  knitr::kable()
} else{
  print("> There is not column without duplicated values")
}

```

- uniform

```{r}
#| echo: false

ss <- inputData |>
  select(everything()) |>
  sapply(isUniform) 

if(length(which(ss))){
  data.frame(
    Variable = names(ss),
    Uniform = unname(ss)
  ) |>
  knitr::kable()
} else{
  cat("There is not column without uniformly distributed")
}
```

\newpage

## Correlation

- Considered only **Numeric** values.

```{r}
#| echo: false
#| warning: false
#| message: false

if (inputData %>% select(where(is.numeric)) %>% length() < 2) {
  cat("Correlation plot ignored, because less than 2 column is numeric")
} else {
  ggcorr(inputData)
}
```

\newpage

## Pairplot

- see distribution and correlation along values.

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: pair

infer.numeric <- function(i, count = 10) {
  length(unique(i)) > count
}

scatterData <- inputData |> 
  select(where(is.numeric) & where(infer.numeric))

if(ncol(scatterData)> 10){
  cat("Data has more than 10 colums, so most various 10 column selected to plot")
  scatterData <- scatterData |> 
    select(
      names(head(sort(sapply(scatterData, function(i){
        length(unique(i))}), decreasing = TRUE), 10))
    )
}

if (!(scatterData |> length() > 0)) {
  cat("Data is not appropriate for Pairplot")
} else {
  if (nrow(scatterData) > 1000) {
    cat("Number of Row Reduced to 1000")
    scatterData <- scatterData |>
      sample_n(1000)
  }
  scatterData |>
    GGally::ggpairs()
}
```

\newpage

## suggestion

1. Check value types: 

- Some **Numeric** value should be change into **Factor** type.

2. Remove unusable values. 

- Identifying values (ID, Name...)

- Outlier / Missing values

- Duplicated values.

- Too various values. (that doesn't show any trend)

3. Define new features with feature engineering.


