---
title: "Title"
author: "(Author)$^{1,*}$"
csl: nature.csl
output:
  word_document:
    fig_height: 6
    fig_width: 9
    reference_docx: doc_ref.docx
  html_document:
    code_folding: hide
    fig_height: 6
    fig_width: 9
    highlight: textmate
    theme: cosmo
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: no
    dev: jpeg
  pdf_document:
    fig_height: 6
    fig_width: 9
header-includes: \usepackage{kotex} \usepackage[doublespacing]{setspace}  \usepackage{multirow}
bibliography: report-paper.bib
editor_options: 
  chunk_output_type: console
  markdown: 
    wrap: 72
params:
  inputData: NA
  MLResult: "MLResult not Available"
---

```{=html}
<style>
   p {line-height: 2.5em;}
</style>
```
```{r setup, include=FALSE}
inputData <- params$inputData
library(ggplot2);library(ggpie);library(GGally);library(naniar);library(dplyr)
library(knitr);library(reshape2);library(grid);library(gridExtra)
library(scales);library(dplyr);library(data.table)

opts_chunk$set(echo = F,fig.align="center",message=FALSE, warning=FALSE,fig.height = 7,cache=T,dpi=300,fig.path = 'figures/')

reverselog_trans <- function(base = exp(1)) {
    trans <- function(x) -log(x, base)
    inv <- function(x) base^(-x)
    trans_new(paste0("reverselog-", format(base)), trans, inv, 
              log_breaks(base = base), 
              domain = c(1e-100, Inf))
}
```

**1** (Affiliation)

$\ast$ Correspondence:

(Name, Degree)

(Affiliation)

* (Address)

Tel: (Tel)

Fax: (Fax)

E-mail: [(Email)](mailto:<Email>){.email}

**keywords** : (Keywords)

## Abstract

(Abstract)

## Introduction

(Introduction)

## Data

```{r}
ignoreNA <- names(which(colSums(is.na(inputData)) == nrow(inputData)))
if (length(ignoreNA) > 0) {
  print("* Columns Below is removed because every rows are NA")
  print(ignoreNA)
  inputData <- inputData[, !(names(inputData) %in% ignoreNA)]
}
```

### MissingData

```{r, echo = FALSE, warning = FALSE, message = FALSE}
missingData <- naniar::miss_var_summary(inputData) %>% filter(n_miss > 0)
knitr::kable(missingData)
```

### Data Attributes
```{r, results='asis', echo = FALSE, warning = FALSE, message = FALSE}
for (i in 1:length(inputData)) {
  count <- inputData %>%
    group_by(inputData[, i]) %>%
    summarise(n = n()) %>%
    mutate(com_freq = cumsum(n)) %>%
    mutate(percent = (n / sum(n)) * 100)

  names(count)[1] <- c("cat")

  colName <- names(inputData)[i]
  uniqcnt <- c("Unique non-mission value count:", length(count[, 1][!is.na(count[, 1])]))
  misscnt <- c("Missing value count:", sum(is.na(count[, 1])))
  table <- data.frame()
  table <- rbind(table, uniqcnt)
  table <- rbind(table, misscnt)
  names(table) <- c(paste(i, "Column name:"), colName)
  print(kable(table, align = "ll"))

  if (length(count[, 1][!is.na(count[, 1])]) <= 10) {
    print(kable(count, align = "cccc"))
  } else {
    data <- data.frame()
    summ <- c(
      min(inputData[, i][!is.na(inputData[, i])], na.rm = TRUE),
      mean(inputData[, i][!is.na(inputData[, i])], na.rm = TRUE),
      median(inputData[, i][!is.na(inputData[, i])], na.rm = TRUE),
      max(inputData[, i][!is.na(inputData[, i])], na.rm = TRUE),
      sd(inputData[, i][!is.na(inputData[, i])], na.rm = TRUE) %>% as.Date(origin = .Date(0))
    )
    data <- rbind(data, summ)
    names(data) <- c("Min", "Mean", "Median", "Max", "SD")
    print(kable(data, align = "ccccc"))
  }
  # cat('---')
  # cat('\n\n\n\n')
  # cat('\n\n<!-- -->\n\n')
}
```

## Body Paragraph 1

### First Point about Topic

(First Point about Topic)

### Second Point about Topic

(Second Point about Topic)

## Body Paragraph 2

### First Point about Topic

(First Point about Topic)

### Second Point about Topic

(Second Point about Topic)

## Discussion

(Discussion)

## Figures

### Correlation

```{r, echo = FALSE, warning = FALSE, message = FALSE}
if (inputData %>% select(where(is.numeric)) %>% length() < 2) {
  print("Correlation plot is ignored because less than 2 column is numeric")
} else {
  ggcorr(inputData)
}
```

### MissingData

```{r}
naniar::gg_miss_var(inputData)
```

### Scatterplot
```{r, results='asis', echo = FALSE, warning = FALSE, message = FALSE}
if (!(inputData %>% select(where(is.numeric)) %>% length() > 0)) {
  print("Non-numeric Variable ignored in Scatterplot below.")
} 
scatterData <- inputData %>% select(where(is.numeric))
if(nrow(inputData)>1000){
  print("Number of Row Reduced to 1000")
  scatterData <- scatterData %>% sample_n(1000)
}
for (i in 1:(ncol(scatterData) %/% 5 + 1)) {
  start <- i * 5 - 4
  if (i == (ncol(scatterData) %/% 5) + 1) {
    end <- ncol(scatterData)
  } else {
    end <- i * 5
  }

  if (start <= end) {
    plot(scatterData[, c(start:end)])
  }
}

```

### Machine Learning Result

Machine Learning Result is not available.
```{r}
# if(!is.na(MLResult)){
#   print(MLResult)
# } else {
#   return("MLResult not available")
# }
```

## Reference

(Reference)
