---
title: "Supported file formats and Notes"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Supported file formats and Notes

### File extensions and function to read

- csv, txt, xls, xlsx, rds, fst, sas7bdat: will utilize `datamods` function. See [link](https://rdrr.io/cran/datamods/man/import-file.html)

- dta: will use `haven::read_dta`
- rda, rdata: will use `load`.
- sas7bcat: will use `haven::read_xpt`
- sav: will use `haven::read_sav`
- tsv: will use `read.csv(sep='\t')`
- xml: will use `custom function based xml2 library`(check below). **File must consisted with 1 layer**

```{r, eval=FALSE}
xml_to_dataframe <- function(path) {
  xml <- xml2::read_xml(path)
  nodeset <- xml2::xml_children(xml)
  lst <- lapply(nodeset, function(x) {
    tmp <- xml2::xml_text(xml2::xml_children(x))
    names(tmp) <- xml2::xml_name(xml2::xml_children(x))
    return(as.list(tmp))
  })
  result <- as.data.frame(do.call(rbind, lst))

  return(tibble::as_tibble(result))
}
```

- json: will use `jsonlite::fromJSON`. **File must consisted with 1 layer**

**To try example files, see [`examples`](https://github.com/statgarten/door/tree/main/examples) in repository**
